---
title: "Exercise 2"
author: "Wojciech Hardy; Łukasz Nawaro"
date: "3/29/2022"
output: html_document
params:
    season:
      label: "season"
      value: 1
      input: slider
      min: 1
      max: 8
      step: 1
      sep: ""
    printcode: TRUE 
    data: .RData
---

#  **Game of Thrones** *(season `r params$season` )*

```{r, echo= FALSE}
x<- paste0("../Data/season_", params$season,".RData")

```


```{r setup, include=FALSE}
load(x)
```


```{r, echo= FALSE, include=FALSE}

library(Rfast)
```


```{r, echo= FALSE}
first <- Rfast::nth(season_data$viewers, 1, descending = T)

second <- Rfast::nth(season_data$viewers, 2, descending = T)

third <- Rfast::nth(season_data$viewers, 3, descending = T)

fourth <- Rfast::nth(season_data$viewers, 4, descending = T)

first_tit <- season_data[season_data$viewers == first ,]$title

first_dirby <- season_data[season_data$viewers == first ,]$directed_by

first_num <- season_data[season_data$viewers == first ,]$no_season

second_tit <- season_data[season_data$viewers == second ,]$title

second_dirby <- season_data[season_data$viewers == second ,]$directed_by

second_num <- season_data[season_data$viewers == second ,]$no_season

third_tit <- season_data[season_data$viewers == third ,]$title

third_dirby <- season_data[season_data$viewers == third ,]$directed_by

third_num <- season_data[season_data$viewers == third ,]$no_season

fourth_tit <- season_data[season_data$viewers == fourth ,]$title

fourth_dirby <- season_data[season_data$viewers == fourth ,]$directed_by

fourth_num <- season_data[season_data$viewers == fourth ,]$no_season
```



Season `r params$season` of Game of Thrones consisted of `r max(season_data$no_season)` episodes. The show gathered an average of `r mean(season_data$viewers)` MLN first-day TV viewers in the US, with the number growing from `r season_data[season_data$no_season == min(season_data$no_season),]$viewers` to `r season_data[season_data$no_season == max(season_data$no_season),]$viewers` million by the end of the season.

The most popular episode of the season was `r season_data[season_data$viewers == max(season_data$viewers),]$title` , in which:

`r season_data[season_data$viewers == max(season_data$viewers),]$description`

------------------------------------------------------------------------

You can see how the viewership of the episodes changed in Figure 1.

```{r viewers_plot, echo= FALSE}
plot(season_data$viewers, type="l", col="red", lwd=5, xlab = "Episode number", ylab = "1st day TV viewers in the US (millions)")
```

--------


|Episodes number |         title         |       directed by       |    viewership     |
|:---------------:|:---------------------:|:-----------------------:|:-----------------:|
|`r paste(first_num)` | `r paste(first_tit)`  | `r paste(first_dirby)`  | `r paste(first)`  |
|`r paste(second_num)` | `r paste(second_tit)` | `r paste(second_dirby)` | `r paste(second)` |
|`r paste(third_num)`| `r paste(third_tit)`  | `r paste(third_dirby)`  | `r paste(third)`  |
|`r paste(fourth_num)` | `r paste(fourth_tit)` | `r paste(fourth_dirby)` | `r paste(fourth)` |
