---
title: "Exercise 2"
author: "Wojciech Hardy; Łukasz Nawaro"
date: "3/29/2022"
output: html_document
params:
    season:
      label: "season"
      value: 1
      input: slider
      min: 1
      max: 8
      step: 1
      sep: ""
---


```{r, echo= FALSE}
x<- paste0("../Data/season_", params$season,".RData")

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
load(x)
```

Season `r params$season` of Game of Thrones consisted of `r max(season_data$no_season)` episodes. The show gathered an average of `r mean(season_data$viewers)` MLN first-day TV viewers in the US, with the number growing from `r season_data[season_data$no_season == min(season_data$no_season),]$viewers` to `r season_data[season_data$no_season == max(season_data$no_season),]$viewers` million by the end of the season.

The most popular episode of the season was `r season_data[season_data$viewers == max(season_data$viewers),]$title` , in which:

`r season_data[season_data$viewers == max(season_data$viewers),]$description`

------------------------------------------------------------------------

You can see how the viewership of the episodes changed in Figure 1.

```{r viewers_plot}
plot(season_data$viewers, type="l", col="red", lwd=5, xlab = "Episode number", ylab = "1st day TV viewers in the US (millions)")
```




